Climate control for performant HPUs

### 2014-04-10 docs/draft/draft1.tex
add annotations and captions to plots

\usepackage{fixltx2e}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{color, soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\newcommand{\vwm}{$V_{w,n,k}$}
\newcommand{\wm}{$W_{w,n,k}$}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
		\caption{caption here}
		\label{fig:classifier}
	\end{center}
\end{figure*}

@@

Not surprisingly, pairs of treatments in which one primes for culture, and the
other primes for ingredients are easily distinguished.  However, it is quite
surprising that high accuracy is achieved when classifying treatments within 
the same valence (e.g. cultural).  This is especially true in such cases as
the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
($\text{F}_1 = 0.863$), where both treatments also share the priming images in 
common.

@@

\begin{figure}
	\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
	\caption{caption here}
	\label{fig:valence}
\end{figure}

\textbf{Priming orients HPU focus.}
Having established that each treatment does in fact consist of distinguishable 
populations of the HPUs, we next look at the content of labels.  Two of the
root labels in our ontology, \texttt{food} and \texttt{cultural}, map naturally
onto the two concepts that laid behind the design of our priming treatments.
A natural and straightforward expectation is that HPUs from treatments 
$\textsc{cult}_x$ should emit more labels that are ontological descendents of
\texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
emit more labels under $\textsc{food}$.

In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
cultural valence (i.e. descending from \texttt{cultural} in the ontology), and 
the percentage having a food valence. Before making comparisons using this
information, we remark that there is no reason to expect a balance in the 
number of words having cultural or food valence overall.  The $\textsc{ambg}$
treatment, which was designed to promote neither valence, exhibits a
significant fraction of words from both the food and cultural valence, while
significantly favoring the former.

@@

\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
	\caption{caption here}
	\label{fig:specificity}
\end{figure*}

@@

>>>>

\usepackage[font=footnotesize,labelfont=bf]{caption}
\usepackage{fixltx2e}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{color, soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\newcommand{\vwm}{$V_{w,n,k}$}
\newcommand{\wm}{$W_{w,n,k}$}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}

@@

\begin{figure*}
	\begin{center}
		\includegraphics[scale=0.55]{../figs/f1scores.pdf}
		\caption{$F_1$-score for binary classification of HPUs from seperate
			treatments using a naive Bayes classifier.  Each pannel shows
			the performance of the classifier when distinguishing between 
			a basis treatment (inset) and the treatments listed on the 
			abscissa.
		}
		\label{fig:classifier}
	\end{center}
\end{figure*}

@@

Not surprisingly, pairs of treatments in which one primes for culture, and the
other primes for ingredients are easily distinguished.  However, it is quite
surprising that high accuracy is achieved when classifying treatments within 
the same orientation (e.g. cultural).  This is especially true in such cases as
the classification of  $\textsc{cult}_{img}$ and $\textsc{cult}_{fund,img}$
($\text{F}_1 = 0.863$), where both treatments also share the priming images in 
common.

@@

\begin{figure}
	\includegraphics[scale=0.65]{../figs/valenceComparison.pdf}
	\caption{Percentage of labels of a food- or cultural- orientation, or
	both.  In our ontology of labels, a label can have multiple parents. 
	For example \texttt{naan} inherits from both \texttt{food} and 
	\texttt{cultural} through its parent \texttt{indian food}.}
	\label{fig:valence}
\end{figure}

\textbf{Priming orients HPU focus.}
Having established that each treatment does in fact consist of distinguishable 
populations of the HPUs, we next look at the content of labels.  Two of the
root labels in our ontology, \texttt{food} and \texttt{cultural}, map naturally
onto the two concepts that laid behind the design of our priming treatments.
A natural and straightforward expectation is that HPUs from treatments 
$\textsc{cult}_x$ should emit more labels that are ontological descendents of
\texttt{cultural}, while those from the $\textsc{ingr}_x$ treatments should
emit more labels under $\texttt{food}$.

In Fig.~\ref{fig:valence}, we exhibit the percentage of labels having a 
cultural orientation (i.e. descending from \texttt{cultural} in the ontology), and 
the percentage having a food orientation. Before making comparisons using this
information, we remark that there is no reason to expect a balance in the 
number of words having cultural or food orientation overall.  The $\textsc{ambg}$
treatment, which was designed to promote neither orientation, exhibits a
significant fraction of words from both the food and cultural orientation, while
significantly favoring the former.

@@

\begin{figure*}
	\begin{center}
	\includegraphics[scale=0.55]{../figs/specificity2.pdf}
	\caption{Pairwise comparisons of label specificity between different 
	HPU treatments.  Each pannel presents a binary comparison between a 
	basis treatment (inset) and the subject treatments indicated on the 
	abscissa.  A positive specificity score indicates that the subject 
	treatment emitted more specific words than the basis treatment overall.
	In a given comparison, a sample of 50 HPUs from the   
	each treatment was randomly sampled, and the specificity of labels from
	the HPUs of oposing treatments were compared.
	To compare two HPUs, each pair of labels from different HPUs are compared.
	and the specificity score of subject HPU is the number of cases where its
	label is more specific than the subject HPUs, less the number of cases 
	where it is more general. This score is 
	avereaged for all HPU pairings.  Statistical significance is guaged
	by generating a null-comparison between two mutually exclusive subsamples 
	from the basis treatment.  This null-comparison yields a distribution
	of relative specificities whose mean is in principle zero.  The 
	specificity scores are expressed in terms of standard deviations of
	the null-comparison specificities.  
	The dotted lines represent the 95\% confidence interval for rejecting 
	the null Hypothesis that the basis treatment and subject treatment are
	equally specific.
	}
	\label{fig:specificity}
	\end{center}
\end{figure*}

@@

\textbf{In-task priming is stronger than framing.}
Our experimental set-up includes two priming mechanisms: in-task priming, 
produced by varying the first 5 images of the task, as well as what could be
called sidestream priming, in which a fictitious funder is disclosed.
The intention behind this set-up was to enable a direct comparison, and 
our expectation was that in-task priming might produce some fraction of the
effect produced by disclosing the funder.  To our surprise, in-task priming 
produces a much stronger effect.

There is a cautionary lesson here.  In-task priming, which is inherently 
impossible to eliminate is may be far more severe than the more overt causes 
of priming that more routinely attract concern during the design of an 
experiment.   Depending on the final purpos of HPU work products, this may be
quite restrictive.

\textbf{Leveraging priming.}
In a more positive view, the results of our study suggest that the ordering 
of subtasks can be used as a way to direct the focus and attention to detail
by HPUs.  If the designer desires more coarse-grained work-products, this
can be achieved by presenting successive subtasks with high diversity.  On 
the other hand if fine-grained work products are desired, then the designer
should aim to sort subtasks into ``tracks'' that are highly homogeneous,
and assign subsens of the pool of HPUs to specifict tracks.

It is interesting to consider to what extent the output of HPUs can be driven
toward nuanced detail using this technique.  Consider, for example, the 
image labelling platform called the ESP Game.  Here Two HPUs are shown
the same image and in order to derive what are in some sense the moset 
characteristic labels, they are asked to attempt to produce the same labels
for the image.  One could imagine a similar setup, but in which the designer
attempts to produce the set of labels that best covers the semantic space 
occupied by the image, by eliciting labels at coarser and finer levels of 
specificity using the techniques suggested by the present work.
